R code for 'Blood parasite infection causes marginal temporary costs in juvenile birds of prey

### 2025-01-08 MS_physiology_infection.Rmd
delta body condition to condition T1

---
title: "R code for 'Apparent physiological costs of blood parasite infection in the early-life of a vertebrate host - only in highest infections'"
author: "Tony Rinaud, Meinolf Ottensmann, Oliver Krüger & Nayden Chakarov"
output: html_document
---

@@

The raw data is comprised of 276 common buzzard (*Buteo buteo*) individuals. Each individual was sampled twice over the course of the nestling period during the years 2016 and 2018 - 2020. First, the raw data is loaded from the file `physiology_infection_stage_full_wideformat.csv` and re-formatted (scaling variables, reordering factor levels etc.) before downstream analyses:

@@

## Plotting predicted values across infection stages
## -----------------------------------------------------------------------------
Fig_S1A <- ggplot(mod_br) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_br$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = bquote("Breathing rate at T"[1])) + 
  ylim(c(min(mod_br$conf.low) - 1.5,max(mod_br$conf.high) + 1.5)) + 
  geom_errorbar(aes(ymin = mod_br$conf.low,ymax = mod_br$conf.high),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_br$predicted - mod_br$std.error, ymax = mod_br$predicted + mod_br$std.error),
                size = 8, colour = wes_palette("Zissou1",4), width = 0,) + 
  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(), 
        plot.margin = margin(0, 0, 0, 0, "cm"), 
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
  aes(x = 1, y = max(mod_br$conf.high) + 1, xend = 4, yend = max(mod_br$conf.high) + 1)) + 
  geom_text(aes(x = 2.5, y = max(mod_br$conf.high) + 1.5),
  label = "n.s.", size = 5)
```

@@

@@

```{r mixed model body condition}
## Model 
## -----------------------------------------------------------------------------
lmer_bc <- lmer(
  delta_body_condition ~ Diff_Inf_Class + Treatment + Age_in_days + days_resample +
    Sex + Year + (1|Nest),
  data = df)

@@

@@

@@

@@

# Table 1 and Table S3 
## -----------------------------------------------------------------------------
sjPlot::tab_model(
  lmer_br,lmer_bt,lmer_bc,lmer_gr,
  show.ci50 = T ,
  show.stat = T,
  string.stat = "t",
  df.method = "kr",
  show.df=T,
  dv.labels = c(bquote("Breathing rate at T"[1]),
                bquote("Body temperature at T"[1]),
                "\U0394 Body condition",
                "Growth rate"),
  file = "./Tables/Table1_results_lmer_physiological_parameters_p.val_kr_Treatment.html")
```

@@

```{r mixed model body condition change 2}
## Model:
## Note: 
## One Contrast for the Interaction of Infection intensity and treatment
## is not estimatable due to the lack of infection level 4 for the Malarone-group
## -----------------------------------------------------------------------------
lmer_bc_para <- lmer(
  delta_body_condition ~ Infection_intensity.2 + Treatment + Age_in_days + days_resample +
    Sex + Year + (1|Nest), data = df)

@@

@@

```{r summary}
## Create multipanel Figure 4
## -----------------------------------------------------------------------------
fig4 = Fig_4A + Fig_4B + Fig_4C + Fig_4D + plot_annotation(tag_levels = 'a') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
fig4

ggsave(fig4,filename = "./Figs/Fig4_predicted_physio_param_infection_intensities_Treatment.png",units = "px", width = 3700, height = 3700)

## Table 2 
## ----------------------------------------------------------------------------- 
sjPlot::tab_model(
  lmer_br_para,
  lmer_bt_para,
  lmer_bc_para,
  lmer_gr_para,
  show.ci50 = T ,
  show.df = T,
  show.stat = T,
  string.stat = "t",
  p.val = "kr",
  dv.labels = c(bquote("Breathing rate at T"[1]),
                bquote("Body temperature at T"[1]),
                "\U0394 Body condition",
                "Growth rate"),
  file = "./Tables/Table2_results_parasitemia_lmer_physiological_parameters_p.val_kr_Treatment.html")
```

@@

tolres_facets <- 
  ggplot(data = filter(df, !Infection_intensity.2 %in% c(NA,0), !Diff_Inf_Class %in% NA),
         aes(y = delta_body_condition, x = as.numeric(Infection_intensity.2), col = Diff_Inf_Class)) + 
  geom_jitter(size = 2, alpha = 0.5, width=0.2) + 
  geom_line(y=0, linetype='dashed')+
  geom_smooth(alpha = 0.2, size = 1.5, method = 'lm',se = T, width = 0.2) + 
  facet_wrap(facets = 'Diff_Inf_Class') +
  labs(y = "",x = bquote("Parasitemia at T"[1]),
       col = 'Infection stages') + 
  scale_x_continuous(breaks = seq(2,5,1),labels = c("1","2","3","4")) + 
  scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),
                     values = c("#3B9AB2", "#E1AF00", "#F21A00")) + 
  theme_bw()+
  annotate(geom = 'segment', y = -Inf, yend = Inf, color = 'black', x = Inf, xend = Inf, size = 0.5) +
  annotate(geom = 'segment', y = -Inf, yend = Inf, color = 'black', x = -Inf, xend = -Inf, size = 0.5) +
  theme(legend.position = "none", 
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 20),
        strip.text = element_text(face = "bold", size = 16),
        axis.title.x = element_text(vjust= 0.2))

@@

ggsave(fig3,filename = "./Figs/Fig3.2_delta_body_condition_to_parasitemia_second.png",units = "px", width = 3700, height = 1700)
```

@@

figS1 <- Fig_S1A + Fig_S1B + Fig_S1C + Fig_S1D + plot_annotation(tag_levels = 'a') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
figS1

@@

ggsave(figS1,filename = "./Figs/FigS1_predicted_physio_param_infection_stages_Treatment.png",units = "px", width = 3700, height = 3700)

@@

Fig_S2C = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
  aes(Diff_Inf_Class,delta_body_condition) + 
  geom_hline(yintercept = mean(df$delta_body_condition, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "\U0394 Body condition") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size = 2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size = 5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 20), 
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(),
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold"))

@@

Fig_S3C = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
  aes(Infection_intensity.2,delta_body_condition) + 
  geom_hline(yintercept = mean(df$delta_body_condition, na.rm = T), linetype = "dashed") + 
  labs(x = bquote("Parasitemia at T"[1]), y = "\U0394 Body condition") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size = 2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size = 5, show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 20),
        axis.text = element_text(size = 16), 
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold"))

@@

Fig_S4C = plot_model(
  lmer_bc,
  sort.est = T,
  se = T,
  title = "\U0394 Body condition",
  axis.labels =
    rev(c("Year [2020]",
          "Year [2018]",
          "Year [2019]",
          "Sampling interval",
          "Treatment [Malarone] at T0",
          "Age (days) at T1",
          "Increasing parasitemia",
          "Sex [Males]",
          "Peak parasitemia",
          "Decreasing parasitemia")))

@@

Fig_S5C = plot_model(
  lmer_bc_para,
  sort.est = T,
  se = T,
  title = "\U0394 Body condition",
  axis.labels = 
    rev(c("Year [2020]",
          "Year [2018]",
          "Year [2019]",
          "Sampling interval",
          "Parasitemia 1 at T1",
          "Treatment [Malarone] at T0",
          "Age (days) at T1",
          "Sex [Males]",
          "Parasitemia 2 at T1",
          "Parasitemia 3 at T1",
          "Parasitemia 4 at T1")))

>>>>

---
title: "R code for 'Blood parasite infection causes marginal temporary costs in juvenile birds of prey'"
author: "Tony Rinaud, Meinolf Ottensmann, Hugo Pereira, Tim M. Rapp, Kai-Philipp Gladow, Oliver Krüger & Nayden Chakarov"
output: html_document
---

@@

The raw data is comprised of 276 common buzzard (*Buteo buteo*) individuals. Each individual was sampled at least twice over the course of the nestling period during the years 2016 and 2018 - 2020. First, the raw data is loaded from the file `physiology_infection_stage_full_wideformat.csv` and re-formatted (scaling variables, reordering factor levels etc.) before downstream analyses:

@@

mod_br <- mod_br[1:4,]

## Plotting predicted values across infection stages
## -----------------------------------------------------------------------------
Fig_S1A <-

  ggplot(mod_br) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_br$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = bquote("Breathing rate at T"[1])) + 
  ylim(c(min(mod_br$conf.low) - 1.5,max(mod_br$conf.high) + 1.5)) + 
  geom_errorbar(aes(ymin = mod_br$conf.low,ymax = mod_br$conf.high),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_br$predicted - mod_br$std.error, ymax = mod_br$predicted + mod_br$std.error),
                size = 8, colour = wes_palette("Zissou1",4), width = 0,) + 
  geom_point(color = "black", size = 2) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(), 
        plot.margin = margin(0, 0, 0, 0, "cm"), 
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
  aes(x = 1, y = max(mod_br$conf.high) + 1, xend = 4, yend = max(mod_br$conf.high) + 1)) + 
  geom_text(aes(x = 2.5, y = max(mod_br$conf.high) + 1.5),
  label = "n.s.", size = 5)
```

@@

mod_bt <- mod_bt[1:4,]

@@

```{r mixed model delta body condition}
## Model 
## -----------------------------------------------------------------------------
lmer_bc <- lmer(
  delta_body_condition ~ Diff_Inf_Class + Treatment + Age_in_days + days_resample +
    Sex + Year + (1|Nest),
  data = df)

@@

mod_bc <- mod_bc[1:4,]

@@

### Body condition at T1

```{r mixed model body condition - Stages}
## Model 
## -----------------------------------------------------------------------------
lmer_bc2 <- lmer(
  body_condition.2 ~ Diff_Inf_Class + Treatment + Age_in_days + days_resample +
    Sex + Year + (1|Nest),
  data = df)

# Predicted values for each infection stage
mod_bc2 = get_model_data(lmer_bc2,type = 'pred',terms = "Diff_Inf_Class") %>%
  mutate(x = factor(c("Uninfected","Increase","Peak","Decrease"), 
                  levels = c("Uninfected","Increase","Peak","Decrease")))

# Table with sample sizes specific for body condition change data
n3.2 = table(df$Diff_Inf_Class[!is.na(df$body_condition.2)])

mod_bc2 <- mod_bc2 %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",n3.2)), levels = c(paste0(x,"\nn= ",n3.2))))

mod_bc2 <- mod_bc2[1:4,]

Fig_S1C2 =

  ggplot(mod_bc2) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_bc2$predicted, na.rm = T), 
             linetype = "dashed") + 
  labs(x = "", 
       y = "Body condition at T1") + 
  geom_errorbar(aes(ymin = mod_bc2$conf.low,
                    ymax = mod_bc2$conf.high),
                colour = "black",
                size = 2, 
                width = .1) +
  geom_errorbar(aes(ymin = mod_bc2$predicted - mod_bc2$std.error,
                    ymax = mod_bc2$predicted + mod_bc2$std.error),
                size = 8,
                colour = wes_palette("Zissou1",4),
                width = 0,) +
  geom_point(color = "black", 
             size = 2) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, 
               aes(x = 1, 
                   y = max(mod_bc2$conf.high) + 17, 
                   xend = 4, 
                   yend = max(mod_bc2$conf.high) + 17)) + 
  geom_text(aes(x = 2.5, 
                y = max(mod_bc2$conf.high) + 23),
              label = "n.s.", size = 5)
```

@@

mod_gr <- mod_gr[1:4,]

@@

# Table 1 and Table S3 
## -----------------------------------------------------------------------------
sjPlot::tab_model(
  lmer_br,lmer_bt,lmer_bc2,lmer_gr,
  show.ci50 = T ,
  show.stat = T,
  string.stat = "t",
  df.method = "kr",
  show.df=T,
  dv.labels = c(bquote("Breathing rate at T"[1]),
                bquote("Body temperature at T"[1]),
                bquote("Body condition at T"[1]),
                "Growth rate"),
  file = "./Tables/Table1_results_lmer_physiological_parameters_p.val_kr_Treatment2.html")
```

@@

```{r mixed model delta body condition change 2}
## Model:
## Note: 
## One Contrast for the Interaction of Infection intensity and treatment
## is not estimatable due to the lack of infection level 4 for the Malarone-group
## -----------------------------------------------------------------------------
lmer_bc_para <- lmer(
  delta_body_condition ~ Infection_intensity.2 + Treatment + Age_in_days + days_resample +
    Sex + Year + (1|Nest), data = df)

@@

### Body condition at T1

```{r mixed model body condition - Parasitemia}
## Model:
## Note: 
## One Contrast for the Interaction of Infection intensity and treatment
## is not estimatable due to the lack of infection level 4 for the Malarone-group
## -----------------------------------------------------------------------------
lmer_bc_para2 <- lmer(
  body_condition.2 ~ Infection_intensity.2 + Treatment + Age_in_days + days_resample +
    Sex + Year + (1|Nest), data = df)

## Rerun without intercept for plotting mean estimates 
## -----------------------------------------------------------------------------
lmer_bc_para_no_intercept2 <- lmer(
  body_condition.2 ~ 0+ Infection_intensity.2 + Treatment + Age_in_days + days_resample +
    Sex + Year + (1|Nest), data = df)

## Obtain effect sizes for post-treatment parasitemia and derive model predictions
## -----------------------------------------------------------------------------
mod_bc_para2 <- 
  left_join(plot_model(lmer_bc_para_no_intercept2, se = F, )[["data"]][1:5,], ## 95% CI
            plot_model(lmer_bc_para_no_intercept2, se = T, )[["data"]][1:5,]) %>%  ## SE
  mutate(predicted = estimate) %>% 
  mutate(lower_CI = conf.low) %>% 
  mutate(higher_CI = conf.high) %>% 
  mutate(se = std.error) %>% 
  mutate(x = factor(c("0","1","2","3","4"), levels = c("0","1","2","3","4")))

# Table with sample sizes specific for body condition change data
m3.2 = table(df$Infection_intensity.2[!is.na(df$body_condition.2)])

mod_bc_para2 <- mod_bc_para2 %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",m3.2)), levels = c(paste0(x,"\nn= ",m3.2))))

Fig_4C2 = ggplot(mod_bc_para2) + 
  aes(as.factor(mod_bc_para2$x),
      mod_bc_para2$predicted) + 
  geom_hline(yintercept = mean(mod_bc_para2$predicted, na.rm = T), 
             linetype = "dashed") + 
  labs(x = bquote("Parasitemia at T"[1]),
       y = "Body condition at T1") + 
  geom_errorbar(aes(ymin = mod_bc_para2$lower_CI, 
                    ymax = mod_bc_para2$higher_CI),
                colour = "black",
                size = 2, 
                width = .1) + 
  geom_errorbar(aes(ymin = mod_bc_para2$predicted - mod_bc_para2$se,
                    ymax = mod_bc_para2$predicted + mod_bc_para2$se),
                size = 8, 
                colour = wes_palette("Zissou1",5), 
                width = 0,) + 
  geom_point(color = "black", 
             size = 4) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 20),  
        axis.title.x = element_text(size = 20, 
                                    vjust=-0.5),
        axis.text = element_text(size = 16), 
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), 
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, 
                                  face = "bold")) + 
  geom_segment(size = .8,
                 aes(x = 1, y = 60, xend = 5, yend = 60)) + 
    geom_text(aes(x = 3, y = 67),
              label = "P = 0.026", size = 5) + 
  geom_segment(size = .8,
                 aes(x = 1, y = 60, xend = 1, yend = 53)) + 
  geom_segment(size = .8,
                 aes(x = 5, y = 60, xend = 5, yend = 53))
```

@@

```{r summary}
## Create multipanel Figure 4
## -----------------------------------------------------------------------------
fig4 = Fig_4A + Fig_4B + Fig_4C2 + Fig_4D + plot_annotation(tag_levels = 'a') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
fig4

ggsave(fig4,filename = "./Figs/Fig4_predicted_physio_param_infection_intensities_Treatment2.png",units = "px", width = 3700, height = 3700)

## Table 2 
## ----------------------------------------------------------------------------- 
sjPlot::tab_model(
  lmer_br_para,
  lmer_bt_para,
  lmer_bc_para2,
  lmer_gr_para,
  show.ci50 = T ,
  show.df = T,
  show.stat = T,
  string.stat = "t",
  p.val = "kr",
  dv.labels = c(bquote("Breathing rate at T"[1]),
                bquote("Body temperature at T"[1]),
                bquote("Body condition at T"[1]),
                "Growth rate"),
  file = "./Tables/Table2_results_parasitemia_lmer_physiological_parameters_p.val_kr_Treatment2.html")
```

@@

tolres_facets <- 
  ggplot(data = filter(df, !Infection_intensity.2 %in% c(NA,0), !Diff_Inf_Class %in% NA),
         aes(y = delta_body_condition, x = as.numeric(Infection_intensity.2), col = Diff_Inf_Class)) + 
  geom_jitter(size = 2, alpha = 0.5, width=0.2) + 
  geom_line(y=0, linetype='dashed')+
  geom_smooth(alpha = 0.3, size = 1.5, method = 'lm',se = T, width = 0.2) + 
  facet_wrap(facets = 'Diff_Inf_Class') +
  labs(y = "",x = bquote("Parasitemia at T"[1]),
       col = 'Infection stages') + 
  scale_x_continuous(breaks = seq(2,5,1),labels = c("1","2","3","4")) + 
  scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),
                     values = c("#3B9AB2", "#E1AF00", "#F21A00")) + 
  theme_bw()+
  annotate(geom = 'segment', y = -Inf, yend = Inf, color = 'black', x = Inf, xend = Inf, size = 0.5) +
  annotate(geom = 'segment', y = -Inf, yend = Inf, color = 'black', x = -Inf, xend = -Inf, size = 0.5) +
  theme(legend.position = "none", 
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 20),
        strip.text = element_text(face = "bold", size = 16),
        axis.title.x = element_text(vjust= 0.2))

@@

ggsave(fig3,filename = "./Figs/Fig3.2_delta_body_condition_to_parasitemia_second.png",units = "px", width = 3700, height = 1700)

## Comparing means parasitemia X stages
df %>% mutate(para_stage=factor(paste(df$Infection_intensity.2,df$Diff_Inf_Class,sep='_'), levels=c('1_Increase',"2_Increase","2_Peak","3_Increase","3_Peak",'4_Increase','4_Peak','3_Decrease',"2_Decrease","1_Decrease", "0_Decrease")))  %>% 
  mutate(treat_stage=factor(paste(df$Treatment,df$Diff_Inf_Class,sep='_'))) -> df

ggplot(df)+
  aes(para_stage,delta_body_condition)+
  geom_boxplot()+
  geom_jitter()+
  stat_n_text()+
  geom_hline(yintercept = mean(df$delta_body_condition), linetype = 2)+
  geom_hline(yintercept = 0,colour = 'red')+
  stat_compare_means(ref.group = ".all.",hide.ns = T,method = "t.test")

## Comparing physio parameters between sucessfully treated and rest

comp=list(c("Malarone_Decrease","Malarone_not_decrease"),c("Malarone_Decrease","Malarone_Uninfected"),c("Malarone_not_decrease", "Malarone_Uninfected"))

ggplot(df)+
    aes(treat_stage, delta_body_condition)+
    geom_hline(yintercept = mean(df$delta_body_condition), linetype = 2)+
    geom_hline(yintercept = 0,colour = 'red')+
    stat_n_text()+
    geom_boxplot()+
    stat_compare_means(comparisons = comp)

ggplot(df)+
    aes(treat_stage, Breathing_rate)+
    geom_hline(yintercept = mean(df$Breathing_rate), linetype = 2)+
    geom_hline(yintercept = 0,colour = 'red')+
    stat_n_text()+
    geom_boxplot()+
    stat_compare_means(comparisons = comp)

ggplot(df)+
    aes(treat_stage, body_temperature)+
    geom_hline(yintercept = mean(df$body_temperature), linetype = 2)+
    geom_hline(yintercept = 0,colour = 'red')+
    stat_n_text()+
    geom_boxplot()+
    stat_compare_means(comparisons = comp)

ggplot(df)+
    aes(treat_stage, Growth_rate)+
    geom_hline(yintercept = mean(df$Growth_rate), linetype = 2)+
    geom_hline(yintercept = 0,colour = 'red')+
    stat_n_text()+
    geom_boxplot()+
    stat_compare_means(comparisons = comp)
```

@@

figS1 <- Fig_S1A + Fig_S1B + Fig_S1C2 + Fig_S1D + plot_annotation(tag_levels = 'a') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
figS1

@@

ggsave(figS1,filename = "./Figs/FigS1_predicted_physio_param_infection_stages_Treatment2.png",units = "px", width = 3700, height = 3700)

@@

Fig_S2C = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
  aes(Diff_Inf_Class,body_condition.2) + 
  geom_hline(yintercept = mean(df$body_condition.2, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Body condition at T1") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size = 2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size = 5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 20), 
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(),
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold"))

@@

Fig_S3C = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
  aes(Infection_intensity.2,body_condition.2) + 
  geom_hline(yintercept = mean(df$body_condition.2, na.rm = T), linetype = "dashed") + 
  labs(x = bquote("Parasitemia at T"[1]), y = bquote("Body condition at T"[1])) + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size = 2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size = 5, show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 20),
        axis.text = element_text(size = 16), 
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold"))

@@

Fig_S4C = plot_model(
  lmer_bc2,
  sort.est = T,
  se = T,
  title = "Body condition at T1",
  axis.labels =
    rev(c("Year [2020]",
          "Year [2018]",
          "Year [2019]",
          "Sampling interval",
          "Treatment [Malarone] at T0",
          "Age (days) at T1",
          "Increasing parasitemia",
          "Sex [Males]",
          "Peak parasitemia",
          "Decreasing parasitemia")))

@@

Fig_S5C = plot_model(
  lmer_bc_para2,
  sort.est = T,
  se = T,
  title = "Body condition at T1",
  axis.labels = 
    rev(c("Year [2020]",
          "Year [2018]",
          "Year [2019]",
          "Sampling interval",
          "Parasitemia 1 at T1",
          "Treatment [Malarone] at T0",
          "Age (days) at T1",
          "Sex [Males]",
          "Parasitemia 2 at T1",
          "Parasitemia 3 at T1",
          "Parasitemia 4 at T1")))
